Range shift literature review

### 2018-12-05 range-shift-lit.Rmd
additional range shift ref

##--> Many organisms must "adapt, move, or die"
--when the environment changes, if they are to persist, organisms must be able to cope with change, change themselves, or move ([@maggini_are_2011])

@@

- but climate velocity was found to explain shifts better than species traits for a range of marine taxa ([@pinsky2013]); however methods used in this study may not have accounted fully for changes in the spatial distribution of survey effort in all cases ([@thorson_model-based_2016])

>>>>

##Many organisms must "adapt, move, or die"
--when the environment changes, if they are to persist, organisms must be able to cope with change, change themselves, or move ([@maggini_are_2011])

@@

--but climate velocity was found to explain shifts better than species traits for a range of marine taxa ([@pinsky2013]); however methods used in this study may not have accounted fully for changes in the spatial distribution of survey effort in all cases ([@thorson_model-based_2016])

--even statistically and biologically significant models based on species traits can have limited exlanatory power and therefore conservation value ([@angert_species_2011])
